Fractional anisotropy as a tracer of cosmic voids

### 2014-09-17 cosmic_voids.tex
New figures, Fractional Anisotropy and Prolatenes for a random sample of the simulation
Improved FA-prolatenes figure
Codes to plot velocity, figures of radial profiles and updated notebook

%.........................................................................
%FIGURE 4: volume functions
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 5: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG.pdf}
  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG.pdf}
  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}

  \captionof{figure}{\small Density profiles of voids for each finding 
  scheme.}

@@

%.........................................................................
%FIGURE 5: shape-distributions
\begin{flushleft}
\begin{figure*}
\centering

>>>>

%.........................................................................
%FIGURE 3: FA of some regions and shape illustration
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/FA_Prolatenes.png}

  \captionof{figure}{\small }

%.........................................................................
%FIGURE 5: volume functions
\begin{flushleft}
\begin{figure*}
\centering

@@

%.........................................................................
%FIGURE 6: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}

  \

  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_VwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}

  \captionof{figure}{\small Density and velocity profiles of voids for 
  each finding scheme.}

@@

%.........................................................................
%FIGURE 7: shape-distributions
\begin{flushleft}
\begin{figure*}
\centering
